---
title: "STAT 425 Final Project"
author: "Michael Garbus mgarbus2"
date: "12/13/2021"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Company XX is a manufacturer of several types of protective packaging, including bubble wrap
sold in both retail and bulk. The objective of this project is to determine the best operating
conditions for the bubble wrap lines to increase production capacity.

The response variable was the production rate measured in lbs/hr. The experiment was
replicated 3 times and the randomization order for each replication was also recorded.


# How to account for replication in model?

```{r}
bubblewrap <- read.csv('bubblewrap.csv') 
```

```{r}
# set factors
bubblewrap$line_speed <- as.factor(bubblewrap$line_speed)
bubblewrap$loading <- as.factor(bubblewrap$loading)
head(bubblewrap)
```

```{r}
#Means
aov_model <- aov(rate ~ -1 + loading + line_speed, data = bubblewrap)
group_means <- aov(rate ~ -1 + loading + line_speed, data = bubblewrap)
```

```{r}
par(mfrow = c(1,2))
boxplot(rate ~ loading, data = bubblewrap)
boxplot(rate ~ line_speed, data = bubblewrap)
```
Loading 4 and Line Speed 37 seem to have different means than their counterparts.

#Todo: Fix Margins
```{r}
loading_and_line_plot <- interaction.plot(x.factor = bubblewrap$loading, response = bubblewrap$rate, trace.factor = bubblewrap$line_speed, fun = mean, col = c('red4','darkblue','darkgreen'), trace.label = "Loading Type", xlab = "Rate", ylab = "Line Speed")
line_and_loading_plot <- interaction.plot(trace.factor = bubblewrap$loading, response = bubblewrap$rate, x.factor = bubblewrap$line_speed, fun = mean, col = c('red4','darkblue','darkgreen'), trace.label = "Rate", xlab = "Loading Type", ylab = "Line Speed")
```
#Modelling


